%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Alation} % Organization
    {alation.com} % Link    
    {Software Engineer} % Job title
    {Provo, UT} % Location
    {2025-05–Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building the user interface for Alation’s AI platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Numbers Station} % Organization
    {numbersstation.ai} % Link    
    {Software Engineer} % Job title
    {Menlo Park, CA} % Location
    {2022-06–2025-05} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped build the company from day one through acquisition by Alation.}
        \item {Led frontend: design, testing, CI/CD, hiring, tooling, framework decisions.}
        \item {Built the user interface for a state-of-the-art machine learning platform.}
        \item {Mentored two other engineers to accelerate career-growth and skill development.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Roote Foundation} % Organization
    {roote.co} % Link    
    {Founding Engineer} % Job title
    {San Francisco, CA} % Location
    {2022-03–2022-08} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed \href{https://github.com/rooteco/tweetscape}{a web app} for interacting with articles and the tweets about them.}
        \item {Harnessed \href{https://hive.one}{Hive} and \href{https://feed.rekt.news/parlor}{Rekt} rankings to categorize tweet and article feeds.}
        \item {Built an engine to sync data between Twitter and a Postgres database.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tutorbook} % Organization
    {tutorbook.org} % Link    
    {Software Engineer} % Job title
    {Palo Alto, CA} % Location
    {2019-02–2022-07} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created \href{https://github.com/tutorbookapp/tutorbook}{a web app} used by schools and nonprofits to connect students with volunteer tutors and mentors.}
        \item {Worked with two schools and three nonprofits that serve over 5000 students and 1000 volunteers.}
        \item {Drafted a privacy policy and a terms of use compliant with California's CSDPA v2.}
        \item {Configured continuous integration for and wrote Cypress tests (74\% code coverage).}
        \item {Contributed to open-source libraries such as React, Next.js, RMWC, and the Firebase SDK.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Hammock} % Organization
    {readhammock.com} % Link    
    {Software Engineer} % Job title
    {San Francisco, CA} % Location
    {2021-04–2021-12} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed \href{https://github.com/nicholaschiang/hammock}{a web app} where you can enjoy reading and learning from newsletters.}
        \item {Decreased LCP by migrating client-side business logic to serverless API functions.}
        \item {Worked with Google's OAuth2, People, and Gmail APIs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Stanford University} % Organization
    {sing.stanford.edu} % Link    
    {Research Intern} % Job title
    {Palo Alto, CA} % Location
    {2018-09–2019-05} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a methodology for building hardware component knowledge bases using machine-learning.}
        \item {Extracted both textual and non-textual information to create relational databases for hardware components.}
        \item {Produced application studies that highlight how these databases make hardware component selection easier.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
