%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Interests}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Eagle Scout Candidate} % Affiliation/role
    {Boy Scouts of America} % Organization/group
    {Palo Alto, CA} % Location
    {Jan. 2016 - Jan. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in life-saving, first-aid, mountaineering,
		canoeing, camping, hiking, cycling, swimming and teamwork.}
        \item {Participated in BSA merit badge camps and high adventure treks.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Brown Belt Instructor} % Affiliation/role
    {Silicon Valley Karate} % Organization/group
    {Palo Alto, CA} % Location
    {Jan. 2016 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Contributed to the intruction of lower belt levels during group
		seminars and/or training.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Photographer, Filmmaker, Musician} % Affiliation/role
    {Qolor Media} % Organization/group
    {San Francisco, CA} % Location
    {Jun. 2019 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Shot and edited professional portraits, video advertising, and
		clothing lookbooks for a variety of different clients.}
        \item {Established a notable YouTube and Instagram media presence.}
        \item {Produced a collection of privately-held drumkits and the
		beginnings of a soon-to-be-released album.}
        \item {Wrote and performed all of the songs included in that
		soon-to-be-released album.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cellist} % Affiliation/role
    {Sono Strings} % Organization/group
    {Mountain View, CA} % Location
    {Jan. 2006 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Performed and recorded the Saint Saens Cello Concerto, Popper's
		Hungarian Rhapsody, Popper's Tarentella, and much more.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
