%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Life Ambitions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
My plans for high school and beyond are probably different from the dreams and
	ambitions of most aspiring Silicon Valley teenagers. I plan to graduate
	early from Henry M. Gunn High School and leave on a two-year-long
	mission for the Church of Jesus Christ of Latter-Day Saints after the
	first semester of my senior year. After that mission, my long-term plan
	is practically identical to that of any other techy: get into a
	prestigious university (right now, I'm aiming for a double major at one
	of the UCs), make friends, meet somebody, graduate with honors, get a
	well-paying job, and settle down for the rest of my life with somebody
	that I love to take on the ultimate challenge of cultivating a
	successful and loving family.
\end{cvparagraph}
\begin{cvparagraph}
Though right now, with my needs more or less taken care of, I can take more
	risks and endeavor to do much more than I might be able to if I didn't
	have the living situation that I do (e.g. I don't have to worry about
	food, rent, bills, taxes, or anything that encumbers adults these days).
	So, I've been busy. Freshman year at Gunn marked the start of what I
	like to call real life. Freshman year I started working at Stanford with
	a pHD candidate on machine learning. Freshman year I created Tutorbook
	(the online tutor-booking platform that is now in use across the Palo
	Alto Unified School District) for my Eagle Scout service project.
	Freshman year I actually started making friends with people that I might
	even stay in touch with after high school and beyond. Freshman year I
	finally passed my Shotokan Karate promotion test and earned the rank of
	4 kyu (brown belt). Freshman year I started a media production "company"
	to cultivate my photography, filmmaking, and music production skills. A
	lot has happened since I first stepped foot on Gunn campus, and
	fortunately for me, most for the better.
\end{cvparagraph}
\begin{cvparagraph}
School has never really been a struggle for me. Maintaining a sense of
	balance has been. I expect myself to be the best at everything - I want to be
	able to start something brand new and excel at it - an expectation that
	clearly isn't realistic and only brings frustration. An expectation that
	can never really be obtained - and thus it is a constant chase, a
	constant striving for perfection that drives me. And I love it. I love
	the exhilarating feeling of success and the rushing urgency of failure.
	I love walking past the library and seeing people I know use Tutorbook.
	I love sharing my creations with others - being able to observe their
	responses and judge for myself what works and what doesn't. But it's
	never enough. There is always something more to be obtained, some new
	goal to be met, some new market to penetrate. The chase is implacable
	just as my desires for success are insatiable. It's an ambition that I
	hope to never lose. An ambition that defines who I am.
\end{cvparagraph}
\begin{cvparagraph}
See below for a list of notable achievements, honors, awards, and leadership
	roles.
\end{cvparagraph}
